Classless Java

### 2015-09-09 paper/paper.tex
added text: return type refinement
point example

%{\theorembodyfont{\sffamily} \newtheorem{theorem}{Theorem}}
%{\theorembodyfont{\sffamily} \newtheorem{lemma}{Lemma}}
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newenvironment{proof}{\textbf{Proof:\hspace{4mm}}}{$\Box$}
\newcommand{\authornote}[3]{{\color{#2} {\sc #1}: #3}}
\newcommand\william[1]{\authornote{william}{green}{#1}}
%%\newcommand\tom[1]{\authornote{tom}{red}{#1}}
\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
\newcommand\yanlin[1]{\authornote{yanlin}{green}{#1}}
%%\newcommand\bruno[1]{}

\newcommand{\hl}[1]{\textcolor{red}{#1}}

@@

%\renewcommand{\mathindent}{0pt}

@@

* Maybe use Marco's example.

@@

>>>>

%{\theorembodyfont{\sffamily} \newtheorem{theorem}{Theorem}}
%{\theorembodyfont{\sffamily} \newtheorem{lemma}{Lemma}}
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newenvironment{proof}{\textbf{Proof:\hspace{4mm}}}{$\Box$}
\newcommand{\authornote}[3]{{\color{#2} {\sc #1}: #3}}
\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
\newcommand\yanlin[1]{\authornote{yanlin}{green}{#1}}
\newcommand{\hl}[1]{\textcolor{red}{#1}}

@@

\newcommand\mixin{\textbf{@Mixin}}

@@

* Maybe use Marco's example (Point example).

\lstinputlisting[linerange=33-42]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINT

\lstinputlisting[linerange=48-74]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINT_OF

@@

   - vs both: we do automatic return type refinement, which has useful applications 
   (example: Expression Problem)
